---
title: "NTU Exercise1"
author: "Yu Tian"
date: "2022-08-04"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      results = 'markup',
                      fig.width = 4,
                      fig.height = 3,
                      fig.align = 'center',
                      message = F,
                      warning = F)
```

## Package 
```{r}
#package
library(dplyr)

#set seed
set.seed(0623)
```

## Preparation
```{r}
# Read (and import) the full exercise data set into R using read.csv()
data1 <- read.csv(file = 'Data_exercise1.csv')

# view the data example in R
data1 %>% head()
```


## 1. Make a plot using log(budget) on the x-axis and log(gross) on the y-axis.
```{r}
# simple plot
plot(log(data1$budget),   #log(budget) on the x-axis
     log(data1$gross),    #log(gross) on the y-axis
     main = "Plot of log(budget) versus log(gross)",
     xlab = "log(budget)", ylab = "log(gross)")
```


## 2. 
### add legend to the plot. Change the color/shape/size of the dots. 
### make the y-axis lable horizontal  

```{r}
plot(log(data1$budget), log(data1$gross), 
     col = "blue",  # change the color
     pch = 20,  # change the shape
     cex = 0.8,  # change the size
     las = 1,  # make the y-axis lable horizontal
     main = "Plot of log(budget) versus log(gross)",
     xlab = "log(budget)", ylab = "log(gross)")

# add a legend
legend("topleft", "points of log(budget) vs log(gross)", 
       pch = 20, col="blue", 
       pt.cex = 1.2, cex = 0.8)
```


## 3.  
### Pre
```{r}
# package
library(rvest)
library(stringr)

# read the website "Basketball-Reference.com"
BR=read_html('https://www.basketball-reference.com/')
```

### Scrape data (more than 100 observations, e.g. player game points) from Basketball-Reference.com
```{r}
# teams information
teams=BR %>%
  html_nodes("#teams .left a") %>%
  html_text()

teams_link=BR %>%
  html_nodes("#teams .left a")%>% 
  html_attr('href')

teams_info=data.frame(teams,teams_link)
```


```{r}
# all player names by looping over all teams
players_name=c()
for (i in 1:nrow(teams_info)) {
  team_link=paste0('https://www.basketball-reference.com',teams_info$teams_link[i])
  
  BR=read_html(team_link)
  
  players=BR %>%
    html_nodes(".iz+ .left a") %>%
    html_text()
  
  players_link=BR %>%
    html_nodes(".iz+ .left a") %>%
    html_attr('href')
  
  players_name_i=data.frame(players,players_link)
  
  players_name=rbind(players_name,players_name_i)
}
View(players_name)
```


```{r}
# players information by looping all player names
players_info=c()
for (i in 1:nrow(players_name)) {
  player_link=paste0('https://www.basketball-reference.com',
                     players_name$players_link[i])
  
  BR=read_html(player_link)
  
  players_FGP=BR %>%
    html_nodes(".p2 div:nth-child(1) p+ p") %>%
    html_text()
  
  if(length(players_FGP)==0) {
    players_FGP = 0
  }
  
  players_FG3P=BR %>%
    html_nodes(".p2 div:nth-child(2) p+ p") %>%
    html_text()
  
  if(length(players_FG3P)==0) {
    players_FG3P = 0
  }
  
   players_FTP=BR %>%
    html_nodes(".p2 div:nth-child(3) p+ p") %>%
    html_text()
   
   if(length(players_FTP)==0) {
    players_FTP = 0
  }
  
  players_eFGP=BR %>%
    html_nodes(".p2 div:nth-child(4) p+ p") %>%
    html_text()
  
  if(length(players_eFGP)==0) {
    players_eFGP = 0
  }
  
   players_PER=BR %>%
    html_nodes(".p3 div:nth-child(1) p+ p") %>%
    html_text()
   
   if(length(players_PER)==0) {
    players_PER = 0
  }
  
  players_info_i=data.frame(players_name$players[i],
                            as.numeric(players_FGP),
                            as.numeric(players_FG3P),
                            as.numeric(players_FTP),
                            as.numeric(players_eFGP),
                            as.numeric(players_PER))
  
  players_info=rbind(players_info,players_info_i)
}

# view the players information in R
players_info %>% head(15)
```


### Run a regression model to answer a question. (Linear regression)

#### Question: Use players_PER as dependent variable; and players_FGP, players_FG3P, players_FTP, players_eFGP as independent variables. Is there a strong correlation between dependent variable and other independent variables? Does this linear regression model fit the data well?

- * PER: Player Efficiency Rating
- * FGP: Field Goal Percentage
- * FG3P: 3-Point Field Goal Percentage
- * FTP: Free Throw Percentage
- * eFGP: Effective Field Goal Percentage

```{r}
# replace zero(0) with NA and remove the NA value
players_info_1 <- players_info %>% 
  mutate_all(~na_if(., 0.0)) %>%
  na.omit(players_info_1)

# Change columns (variables) name
colnames(players_info_1) <- c("players_name", "players_FGP", "players_FG3P", "players_FTP", "players_eFGP", "players_PER")

players_info_1 %>% head(15)
```


```{r}
# run a linear regression model
lr_players_info <- lm(players_PER ~ players_FGP + players_FG3P + players_FTP + players_eFGP, data = players_info_1)
# show the regression results
summary(lr_players_info)
```
From the p value above, we can find that these coefficient of all independent variable is significant. However, from the R-squared value above, we can find this model id not fitting the data very well.


## 4. Output the results using 'stargazer'
```{r}
# package
library(stargazer)

# output the regression results
stargazer(lr_players_info, type = "text", title = "Linear regression model of player information")
```





